Explicit B-spline regularization in diffeomorphic image registration

### 2013-10-25 paper.tex
ENH: Getting stuff ready for submission.

\begin{figure}[htb]
  \centering
  \begin{tabular}{c}
  \includegraphics[width=0.95\textwidth]{evaluation.jpg}
  \end{tabular}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
  \begin{tabular}{c}
  \includegraphics[width=0.95\textwidth]{evaluation.jpg}
  \end{tabular}
  \caption{Dice results for both algorithms for 
  each subject warped to every other subject using the pseudo-
  geodesic transform.  Each 
  row corresponds to one of the five data sets used for evaluation.
  For each data set we include a plotting of all individual label 
  Dice results by volume and a combined label box plotting.  The
  left and right halves show the results for MALF-derived and 
  original labelings, respectively.
  }
  \label{fig:dice}
\end{figure}
